\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2020-08-07 sections/results.tex
Updates from Overleaf

  \begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figure3.pdf}
    \caption{
      \textbf{The representative sequences generated by the different denoising/clustering methods are very similar but differ in the sequences that are in low abundance.}
      \textbf{(A)} The average weighted UniFrac distance between the representative sequences shows that the representative sequences and their compositions are fairly identical between the methods,
      \textbf{(B)} The relatively larger average unweighted UniFrac distance indicates that methods differ in their identification of sequences of low abundance,
      \textbf{(C, D)} The distributions of the avegage weighted UniFrac distance between the expected sequence profile and the calculated sequence profile in mock datasets.
      \textbf{(D)} The distributions of the average unweighted UniFrac distance show that dada2 and Deblur were the best performing methods in most of the datasets.
    }
    \label{fig:figure3}
  \end{figure}

>>>>

  \begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figure3.pdf}
    \caption{
      \textbf{The representative sequences generated by the different denoising/clustering methods are very similar but differ in the sequences that are in low abundance.}
      \textbf{(A)} The average weighted UniFrac distance between the representative sequences shows that the representative sequences and their compositions are fairly identical between the methods,
      \textbf{(B)} The relatively larger average unweighted UniFrac distance indicates that methods differ in their identification of sequences of low abundance,
      \textbf{(C, D)} The distributions of the average weighted UniFrac distance between the expected sequence profile and the calculated sequence profile in mock datasets.
      \textbf{(D)} The distributions of the average unweighted UniFrac distance show that dada2 and Deblur were the best performing methods in most of the datasets.
    }
    \label{fig:figure3}
  \end{figure}
